Windowed least-squares model reduction for dynamical systems

### 2019-10-18 section4/spatial_numerical.tex
fix 1/2

Direct approaches solve optimization problem~\eqref{eq:tclsrm} by
``transcribing" the infinite-dimensional optimization problem into a finite-dimensional one by discretizing the state and objective functional in time.
The minimization problem is then reformulated as a (non)linear 
optimization problem. A variety of direct solution approaches exist, 
including collocation approaches, spectral  methods, and genetic algorithms.  
In the context of \spatialAcronym\ trial subspaces, the most straightforward direct solution approach consists of the 
following steps: (1) numerically discretize the FOM ODE (and hence the
\textit{integrand} of the objective function in problem~\eqref{eq:obj_gen_slab}) and 
(2) select a numerical quadrature rule to evaluate the \textit{integral}
defining the objective function in~\eqref{eq:obj_gen_slab}.
To this end, we define time grids
$\{\timeWindowArg{n}{i}\}_{i=0}^{\nstepsArg{n}}\subset[\timeStartArg{n},\timeEndArg{n}]$
\EP{Shouldn't this be subset? We can't recover the continuous time interval}
\KTC{Yes},
$n=1,\ldots,\nslabs$ that
satisfy 
$\timeStartArg{n}=\timeWindowArg{n}{0} \le \cdots \le \timeWindowArg{n}{\nstepsArg{n}} 
 = \timeEndArg{n}$. %\KTC{use cdots, not
%hdots or ldots. Don't use $\defeq$ for the first and last times; these are
%just equalities, i.e., you happen to set them equal to those values, but they
%aren't identically the same:}
Figure~\ref{fig:slab_fig2} depicts such a discretization.
For the purposes of indexing between different windows, we additionally define a function:
$$\indexMapper: (n,i) \mapsto 
\begin{cases}
	(n,i) & n \geq 1, \; i \geq 0, \\
\indexMapper(n-1,\nstepsArg{n-1}+i) & n > 1, \; i \le 0.
\end{cases}$$
\KTC{Note: I added parenthesis here because a function can't really map to a
pair of indices unless they are defined as a collection or tuple. Should be
fine.}
We now outline the direct solution approach for linear-multistep schemes; the formulation for
other time-integration methods (e.g., Runge--Kutta) follows closely. 
\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.0cm 4.5cm 0cm 3cm},clip,width=1.0\textwidth]{figs/time_grid_timesteps.pdf} 
	\caption{Depiction of the $\nstepsArg{n}+1$ time instances over each window. In the figure, $\nstepsArg{n} = 2$ for all $n$.} 
\label{fig:slab_fig2} 
\end{centering} 
\end{figure}
%We now outline several commonly employed temporal discretization 
%schemes, specifically linear multistep and collocation (Runge--Kutta) methods, that leverage this time-grid to discretize the FOM ODE and 
%objective functional.

>>>>

Direct approaches solve optimization problem~\eqref{eq:tclsrm} by
``transcribing" the infinite-dimensional optimization problem into a finite-dimensional one by discretizing the state and objective functional in time.
The minimization problem is then reformulated as a (non)linear 
optimization problem. A variety of direct solution approaches exist, 
including collocation approaches, spectral  methods, and genetic algorithms.  
In the context of \spatialAcronym\ trial subspaces, the most straightforward direct solution approach consists of the 
following steps: (1) numerically discretize the FOM ODE (and hence the
\textit{integrand} of the objective function in problem~\eqref{eq:obj_gen_slab}) and 
(2) select a numerical quadrature rule to evaluate the \textit{integral}
defining the objective function in~\eqref{eq:obj_gen_slab}.
To this end, we define time grids
$\{\timeWindowArg{n}{i}\}_{i=0}^{\nstepsArg{n}}\subset[\timeStartArg{n},\timeEndArg{n}]$,
$n=1,\ldots,\nslabs$ that
satisfy 
$\timeStartArg{n}=\timeWindowArg{n}{0} \le \cdots \le \timeWindowArg{n}{\nstepsArg{n}} 
 = \timeEndArg{n}$. %\KTC{use cdots, not
%hdots or ldots. Don't use $\defeq$ for the first and last times; these are
%just equalities, i.e., you happen to set them equal to those values, but they
%aren't identically the same:}
Figure~\ref{fig:slab_fig2} depicts such a discretization.
For the purposes of indexing between different windows, we additionally define a function:
$$\indexMapper: (n,i) \mapsto 
\begin{cases}
	(n,i) & n \geq 1, \; i \geq 0, \\
\indexMapper(n-1,\nstepsArg{n-1}+i) & n > 1, \; i \le 0.
\end{cases}$$
\KTC{Note: I added parenthesis here because a function can't really map to a
pair of indices unless they are defined as a collection or tuple. Should be
fine.}
We now outline the direct solution approach for linear-multistep schemes; the formulation for
other time-integration methods (e.g., Runge--Kutta) follows closely. 
\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.0cm 4.5cm 0cm 3cm},clip,width=1.0\textwidth]{figs/time_grid_timesteps.pdf} 
	\caption{Depiction of the $\nstepsArg{n}+1$ time instances over each window. In the figure, $\nstepsArg{n} = 2$ for all $n$.} 
\label{fig:slab_fig2} 
\end{centering} 
\end{figure}
%We now outline several commonly employed temporal discretization 
%schemes, specifically linear multistep and collocation (Runge--Kutta) methods, that leverage this time-grid to discretize the FOM ODE and 
%objective functional.
